The problem and promise of scale in multilayer animal social networks

### 2020-02-11 paper/manuscript.Rmd
trying to fix citations, some aren't working right

Social network positions are frequently used to represent the social environment
that an individual experiences or their social phenotype. Multilayer networks
provide a way to bridge these different scales so that we can examine social
phenotypes in more holistic ways rather than looking at each scale separately as
has traditionally been done. From a monolayer network perspective, social
phenotypes are increasingly linked to important fitness for individuals of
various species, including primates [@Brent_2017; @Thompson_2019], dolphins
[@Stanton_2012; @Stanton_2011], and birds [@McDonald_2007; @Royle_2012]. Both
social scales, types of interactions, and temporal, seasons and stages of life,
have emerged as important for understanding fitness consequences in the context
of social network positions [@Almeling_2016, @Berger_2015, @Brent_2017,
@Holekamp_2012].

@@

Temporal scale is also important for understanding the repercussions of social
phenotypes. Varying the time window length and position for caribou, we found
there was a lot of variation in the multilayer network metrics (Figure \@ref(fig:winlen), Figure \@ref(fig:winpos)). 
These changes in the outcome depending on how the time window is
defined highlight how critical it is to properly define the time window
appropriately to address the questions and hypotheses of interest. For instance,
social phenotypes can change over ontogeny in ways that can affect fitness
[@Berger_2015, @Brent_2017]. Thus, it is critical to carefully consider the
temporal scale that is meaningful for the proposed hypotheses. Further
complicating the issue of selecting suitable time scales across ontogeny,
individuals progress through development at different rates [@Tarka_2018]. This
variation can make defining appropriate temporal scales for testing the fitness
implications of an individual’s social phenotype over different stages of
ontogeny even more difficult when they vary by individual. However, considering
fine temporal scales provide insight across developmental stages that may
otherwise be missed [@Turner_2018]. Defining temporal scales is a challenge in
multilayer networks just as in monolayer networks; however, multilayer networks
provide metrics that enable researchers to look at similarities and differences
in separate layers representing different stages of ontogeny, or seasons as in
our case study, which can be difficult to detect.

Multilayer networks provide unique opportunities and challenges, linking these
various scales, for understanding the social phenotypes and environments of
individuals and their fitness outcomes. The multilayer network framework enables
researchers to examine these different social scales simultaneously rather than
individually, which is what has been done under most circumstances, but is not
very realistic. Metrics from multilayer networks provide an opportunity to
simplify statistical models. Interactions that happen side-by-side, proximity
associations, and long-distance interactions can be encapsulated in a single
multilayer network, and a single metric can be used to describe the various
social scales of an individual’s network position. This multilevel network
metric could be used to assess the relationship between an individual’s social
phenotype and fitness. It would also be a meaningful simplification of many
network metrics that could help simplify statistical analyses and deal with the
frequent correlations between social network metrics in different types of
networks [@Castles_2014]. Furthermore, multilayer networks provide a framework
to test hypotheses linking social phenotypes and fitness across temporal scales.
Because of the non-independent nature of social interactions and associations,
especially over time, it is hard to test hypotheses about social dynamics with a
suitable null control [@Farine_2017, @Proskurnikov_2017]. Using the framework of
multilayer networks, making layers of different temporal periods provides a way
to make appropriate null models to test questions about the dynamics of an
individual’s social network position over multiple aggregated time periods.

>>>>

Social network positions are frequently used to represent the social environment
that an individual experiences or their social phenotype. Multilayer networks
provide a way to bridge these different scales so that we can examine social
phenotypes in more holistic ways rather than looking at each scale separately as
has traditionally been done. From a monolayer network perspective, social
phenotypes are increasingly linked to important fitness for individuals of
various species, including primates [@Brent_2017; @Thompson_2019], dolphins
[@Stanton_2012; @Stanton_2011], and birds [@McDonald_2007; @Royle_2012]. Both
social scales, types of interactions, and temporal, seasons and stages of life,
have emerged as important for understanding fitness consequences in the context
of social network positions [@Almeling_2016; @Berger_2015; @Brent_2017;
@Holekamp_2011].

@@

Temporal scale is also important for understanding the repercussions of social
phenotypes. Varying the time window length and position for caribou, we found
there was a lot of variation in the multilayer network metrics (Figure \@ref(fig:winlen), Figure \@ref(fig:winpos)). 
These changes in the outcome depending on how the time window is
defined highlight how critical it is to properly define the time window
appropriately to address the questions and hypotheses of interest. For instance,
social phenotypes can change over ontogeny in ways that can affect fitness
[@Berger_2015; @Brent_2017]. Thus, it is critical to carefully consider the
temporal scale that is meaningful for the proposed hypotheses. Further
complicating the issue of selecting suitable time scales across ontogeny,
individuals progress through development at different rates [@Tarka_2018]. This
variation can make defining appropriate temporal scales for testing the fitness
implications of an individual’s social phenotype over different stages of
ontogeny even more difficult when they vary by individual. However, considering
fine temporal scales provide insight across developmental stages that may
otherwise be missed [@Turner_2017]. Defining temporal scales is a challenge in
multilayer networks just as in monolayer networks; however, multilayer networks
provide metrics that enable researchers to look at similarities and differences
in separate layers representing different stages of ontogeny, or seasons as in
our case study, which can be difficult to detect.

Multilayer networks provide unique opportunities and challenges, linking these
various scales, for understanding the social phenotypes and environments of
individuals and their fitness outcomes. The multilayer network framework enables
researchers to examine these different social scales simultaneously rather than
individually, which is what has been done under most circumstances, but is not
very realistic. Metrics from multilayer networks provide an opportunity to
simplify statistical models. Interactions that happen side-by-side, proximity
associations, and long-distance interactions can be encapsulated in a single
multilayer network, and a single metric can be used to describe the various
social scales of an individual’s network position. This multilevel network
metric could be used to assess the relationship between an individual’s social
phenotype and fitness. It would also be a meaningful simplification of many
network metrics that could help simplify statistical analyses and deal with the
frequent correlations between social network metrics in different types of
networks [@Castles_2014]. Furthermore, multilayer networks provide a framework
to test hypotheses linking social phenotypes and fitness across temporal scales.
Because of the non-independent nature of social interactions and associations,
especially over time, it is hard to test hypotheses about social dynamics with a
suitable null control [@Farine_2017; @Proskurnikov_2017]. Using the framework of
multilayer networks, making layers of different temporal periods provides a way
to make appropriate null models to test questions about the dynamics of an
individual’s social network position over multiple aggregated time periods.
